Test susieI using whole genome, s40.22 samples

### 2020-11-19 analysis/simulation-susieI-ukbWG-gtex.adipose_s40.22.Rmd
index
susie different prior variance

The genotype data we used is from UKB biobank, randomly selecting `r as.character(n.ori)` samples. We then filtered samples based on relatedness, ethics and other qc metrics, that ended up with n = `r as.character(n)` samples.  We use SNP genotype data from chr 1 to chr 22 combined from UKB. SNPs are downsampled to 1/10 (randomly), eQTLs (see below for definition of eQTL) were added back. This ends up with p = `p as.charater(p)` SNPs.

@@

  df <- data.frame("ncausal" = nca_mean, "se" = se )

@@

>>>>

The genotype data we used is from UKB biobank, randomly selecting `r as.character(n.ori)` samples. We then filtered samples based on relatedness, ethics and other qc metrics, that ended up with n = `r as.character(n)` samples.  We use SNP genotype data from chr 1 to chr 22 combined from UKB. SNPs are downsampled to 1/10 (randomly), eQTLs (see below for definition of eQTL) were added back. This ends up with p = `r as.character(p)` SNPs.

@@

  df <- data.frame("ncausal" = nca_mean, "se" = se)

@@

## susieI (4)
* Regions: all regions, LD-defined regions.
* Susie run parameters: `L=1`. We use true prior variance and plug into SUSIE, so this should be the same as SER/EM (2). We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes).

```{r param9susie, fig.height=6, fig.width=8}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config9.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config9.susieI.txt")

```{r pip9susie, fig.height=6, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="susie", main = "PIP(low power)" )
f2 <- caliPIP_plot(susieIfs2[6:10], format ="susie", main = "PIP(high power)" )
f3 <- ncausal_plot(susieIfs2[1:5], format = "susie", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "susie", main = "No. Causal Genes (high power)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```

```{r scatter9susie, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```

## susieI (5)
* Regions: all regions, LD-defined regions.
* Susie run parameters: `L=5`. We use true prior variance and plug into SUSIE. We initialize with prior for genes and SNPs as uniform. gene.pve ~ 0.1, snp.pve ~ 0.5.  Null weight is calculated based on prior of genes and SNPs ( 1 - sum of priors for snps and genes).

```{r param10susie, fig.height=6, fig.width=8}
tags <- paste(rep(1:2, each = 5), 1:5, sep = "-")
phenofs <- paste0(simdatadir, "simu_20201001-", tags, "-pheno.Rd")
susieIfs <- paste0(outputdir, "20201001-", tags, ".config10.susieIres.Rd")
susieIfs2 <- paste0(outputdir, "20201001-", tags, ".config10.susieI.txt")

```{r pip10susie, fig.height=6, fig.width=8}
f1 <- caliPIP_plot(susieIfs2[1:5], format ="susie", main = "PIP(low power)" )
f2 <- caliPIP_plot(susieIfs2[6:10], format ="susie", main = "PIP(high power)" )
f3 <- ncausal_plot(susieIfs2[1:5], format = "susie", main = "No. Causal Genes (low power)")
f4 <- ncausal_plot(susieIfs2[6:10], format = "susie", main = "No. Causal Genes (high poweunr)")
gridExtra::grid.arrange(f1, f2, f3, f4, ncol =2)
```

```{r scatter10susie, fig.height=4, fig.width=8}
par(mfrow=c(1,2))
f1 <- scatter_plot_PIP_p(susieIfs2[1:5], gwasfs[1:5], pipformat = "susie", main = "low power")
f2 <- scatter_plot_PIP_p(susieIfs2[6:10], gwasfs[6:10], pipformat = "susie", main = "high power")
```
